Exploratory Plots

### 2020-10-01 exploratory/2020/sub4_fitpercent.Rmd
Use full results tsv

```{r read_join}
dirpath <- 'subworkflows/3_fit_sample_subset/results/all-seqs/'
results <- list.files(here(dirpath)) %>% 
  (function(x) { here(glue('{dirpath}{x}')) }) %>% 
  map(read_tsv) %>% 
  reduce(full_join) %>% 
  mutate(num_total_seqs = num_ref_seqs + num_sample_seqs,
         gaps_frac = n_gaps / total_chars)
head(results)
dim(results)
```

>>>>

```{r read_join}
results <- read_tsv('subworkflows/4_fitpercent/results/full_results.tsv')
head(results)
dim(results)
```
